\section{Introduction}
The aim of this project created for a university course named Cryptography was to create an application for sensitive file sharing. It is designed to be used by 
users who are on the same network and want to share encrypted files without the use of a server, that can be solved using peer-to-peer communication. The application is
written in Python 3.12 with the use of supporting libraries, which will be described later in this introduction. The application is accompanied by a graphical user
interface. It is designed to be used on any operating system that supports Python 3.12 and the required libraries. \\

The required files to run this application are all in this repository. Apart from the \texttt{main.py} file all of the code is in the file\_share directory.
The \texttt{main.py} file is the entry point of the application and is used to start the GUI. As input for the app there is nothing required apart from a file
that a user wants to send. The output is a file that was sent to the user from another user using the app. \\

The application uses the following libraries:
\begin{itemize}
    \item \texttt{Tkinter (v8.6)} - for the Graphical User Interface
    \item \texttt{Uvicorn (v0.27.1)} - used for receiver realisation
    \item \texttt{FastAPI (v0.110.0)} - for the receiver API
    \item \texttt{SQLAlchemy (v2.0.28)} - for the database implementation
    \item \texttt{Cryptography (v42.0.5)} - for encryption and decryption of files
    \item \texttt{AIOHTTP (v3.9.3)} - for communication between the sender and the receiver
\end{itemize}