\section{Application structure}
{\small
%
\dirtree{%.
.1 KRY-Project.
.2 file\_share.
.3 app \DTcomment{Core methods of the application}.
.4 \_\_init\_\_.py.
.4 app.py.
.4 init\_app.py.
.4 test\_send\_file.py.
.3 database \DTcomment{Definitions of all database tables}.
.4 \_\_init\_\_.py.
.4 base.py.
.4 files.py.
.4 keys.py.
.4 me.py.
.4 users.py.
.3 definitions.
.4 \_\_init\_\_.py.
.4 dataclasses.py.
.4 enum.py.
.4 procedures.py.
.3 friend\_finder \DTcomment{Methods to discover and work with users on the network}.
.4 \_\_init\_\_.py.
.4 ping\_em.py.
.3 receiver \DTcomment{Endpoint definitons enabling data reception with authentication}.
.4 \_\_init\_\_.py.
.4 api\_keys.py.
.4 get\_ip.py.
.4 receiver\_api.py.
.3 sender \DTcomment{Methods to send files and work with queue}.
.4 \_\_init\_\_.py.
.4 sender.py.
.4 ssl\_context.py.
.3 \_\_init\_\_.py.
.2 main.py.
.2 pdm.lock \DTcomment{Package data}.
.2 pyproject.toml \DTcomment{Basic configuration file}.
.2 README.md.
.2 testfile.txt.
}
}

\newpage
\section{Conclusion}
This project set out to create a GUI controlled application that enables a secure Peer-to-Peer file transfer on a public network in two modes:
\begin{itemize}
    \item Real-time transmission -- both users are online and the transmission is immediate
    \item Delayed transmission -- the receiving user is offline so the transmission is stored in a~secured storage waiting to be sent once the user becomes available
\end{itemize}
All of the aforementioned goals were achieved using the Python programming language.